### 2019-09-08 Writeup/Paper/sections/background.tex
State at submission

\subsection{Similarity Metrics}
\label{sec:similarity_metric}
A similarity metric is an algorithm designed to determine if two words are phonetically a match. For example, the words ``THEIR" and "THERE" is a match, whereas the words ``DARK" and ``PRINCIPLE" are not phonetically matching. This section provides a base explanation of important phonetic algorithms relevant in this project.

@@

\textbf{Phonetic Vectors} - Phonetic Vectors; created by Allison Parrish in 2017\cite{parrish2017poetic}, is as the name suggests the vectorisation of the phonetics of a word. Phonetic features are used in this work as a way to compare the similarity of phonemes. Phonemes are the phonetic elements that construct a word. For example, the word ``RING" translated into the phonemes \verb|/R IH NG/|.

>>>>

\subsection{Similarity Metrics}
\label{sec:similarity_metric}
A similarity metric is an algorithm designed to determine if two words are phonetically a match. For example, the words ``THEIR'' and ``THERE'' is a match, whereas the words ``DARK'' and ``PRINCIPLE'' are not phonetically matching. This section provides a base explanation of important phonetic algorithms relevant in this project.

@@

\textbf{Phonetic Vectors} - Phonetic Vectors; created by Allison Parrish in 2017\cite{parrish2017poetic}, is as the name suggests the vectorisation of the phonetics of a word. Phonetic features are used in this work as a way to compare the similarity of phonemes. Phonemes are the phonetic elements that construct a word. For example, the word ``RING'' translated into the phonemes \verb|/R IH NG/|.

### 2019-09-08 Writeup/Paper/sections/design.tex
State at submission

\subsection{Attack Design}
\label{sec:attackDesign}
The propossed attack on Trustwords involves generating ``near-collision'' keys. Near-collision keys are keys composed of a set of words that are deemed a match by the similarity metrics.
\\\\
The attack is designed to target a single pair of users and requires recomputation for each attack target pair. Each pair is split into an "Uncontrolled" or "Controlled" key. Uncontrolled is the receiver of the communication, and, thus, the key cannot be altered. The Controlled key is the one we are attempting to impersonate. It is assumed that there is the ability to replace the Controlled key with the malicious option. The uncontrolled and controlled keys can be swapped around, thus, resulting in the possibility to intercept both directions of communication.
\\\\
When attacking, a similarity metric is used to compute a list of possibilities for each position in the target fingerprint. Completing these steps produces a list of fingerprints that can be inserted into a tool designed to hash a large number of keys and search for matches. This aspect of using an extensive list to search for keys massively reduces the complexity of the search.

@@

    \item Select a target and allocate ``Uncontrolled" and ``Controlled" key identification.

>>>>

\subsection{Attack Design}
\label{sec:attackDesign}
The proposed attack on Trustwords involves generating ``near-collision'' keys. Near-collision keys are keys composed of a set of words that are deemed a match by the similarity metrics.
\\\\
The attack is designed to target a single pair of users and requires recomputation for each attack target pair. Each pair is split into an ``Uncontrolled'' or ``Controlled'' key. Uncontrolled is the receiver of the communication, and, thus, the key cannot be altered. The Controlled key is the one we are attempting to impersonate. It is assumed that there is the ability to replace the Controlled key with the malicious option. The uncontrolled and controlled keys can be swapped around, thus, resulting in the possibility to intercept both directions of communication.
\\\\
When attacking, a similarity metric is used to compute a list of possibilities for each position in the target fingerprint. Completing these steps produces a list of fingerprints that can be inserted into a tool designed to hash a large number of keys and search for matches. This aspect of using an extensive list to search for keys massively reduces the complexity of the search.

@@

    \item Select a target and allocate ``Uncontrolled'' and ``Controlled'' key identification.

### 2019-09-08 Writeup/Thesis/chapters/evaluation.tex
State at submission

Research Question 1 asks: \textit{“What are the best performing schemes to quantify phonetic similarity?”}. This paper has discussed several metrics used to quantify phonetic similarity (See Section \ref{sec:metrics}). Most metrics were chosen due to their high utilisation and occurrence in literature. The only exception to this is the presence of Phonetic Vectors. Performance of these metrics were then quantified in a direct study that selected the top three from a set of five (See Section \ref{exp:metric}). These newly selected metrics was then assessed in an attack context with their performance being indirectly quantified (See Section \ref{sec:exp2_design}).

@@

\section{Research Question \ref{goal:attackPercentage}}
Research Question \ref{goal:attackPercentage} \textit{``What percentage of attacks successfully deceive a user?''} was shown by the results presented in Section \ref{sec:exp2}. The weakest attack strength and ones that can be computed by a single mid-range GPU for a single week achieved success rate ranging from 9.35\% - 11.01\%. The middle attack involving the use of 10 mid-range GPUs for a week had success rates of 15.20\% - 19.20\%. Finally, the highest attack strength that theoretically involved the use of 100 mid-range GPUs computing for a week has success rates: 24.43\% - 32.05\%. Therefore, showing the number of attacks required to deceive a set of users.

>>>>

Research Question 1 asks: \textit{“What are the best performing schemes to quantify phonetic similarity?”}. This paper has discussed several metrics used to quantify phonetic similarity (See Section \ref{sec:metrics}). Most metrics were chosen due to their high utilisation and occurrence in literature. The only exception to this is the presence of Phonetic Vectors. Performance of these metrics were then quantified in a direct study that selected the top three from a set of five (See Section \ref{exp:metric}). These newly selected metrics were then assessed in an attack context with their performance being indirectly quantified (See Section \ref{sec:exp2_design}).

@@

\section{Research Question \ref{goal:attackPercentage}}
Research Question \ref{goal:attackPercentage} \textit{``What percentage of attacks successfully deceive a user?''} was shown by the results presented in Section \ref{sec:exp2}. The weakest attack strength and ones that can be computed by a single mid-range GPU for a single week achieved success rate ranging from 9.35\% - 11.01\%. The middle attack involving the use of 70 mid-range GPUs for a week had success rates of 15.20\% - 19.20\%. Finally, the highest attack strength that theoretically involved the use of 700 mid-range GPUs computing for a week has success rates: 24.43\% - 32.05\%. Therefore, showing the number of attacks required to deceive a set of users.

### 2019-09-08 Writeup/Thesis/chapters/experiments.tex
Changes; - Small corrections added
State at submission

Figure \ref{tab:scallion_speed} shows the speed decline as the number of concurrently checked potential keys increases. Alongside the results for base version of Scallion is the speed for \textit{Scallion Improved}. This is the same Scallion code but with a fix that reduces the severity of the speed decline.

@@

As can be seen most notably from Table \ref{tab:nysiis2}, the generation of the actual Trustwords differs in only 3 characters making it arguably very similar. When linking this generated key to results of the second experiment (See Section \ref{sec:exp2}) computation of 2.53 days on a single mid-range GPU can achieve around a 28\% success rate when assessed against actual users. This time, however, has been improved due to the random search for a controlled key with a more favourable number of near-collision keys. Even with the least restricted attack type presented in Table \ref{tab:nysiis0}, the computation of half a day can provide almost a 10\% success rate when attacking users. This results in any user with a single commodity GPU could compute enough keys in less than a week to have a very high probability of deceiving an actual user.

>>>>

Figure \ref{tab:scallion_speed} shows the speed decline as the number of concurrently checked potential keys increases. Alongside the results for the base version of Scallion is the speed for \textit{Scallion Improved}. This is the same Scallion code but with a fix that reduces the severity of the speed decline.

@@

As can be seen most notably from Table \ref{tab:nysiis2}, the generation of the actual Trustwords differs in only 3 characters making it arguably very similar. When linking this generated key to results of the second experiment (See Section \ref{sec:exp2}) computation of 2.93 days on a single mid-range GPU can achieve around a 28\% success rate when assessed against actual users. This time, however, has been improved due to the random search for a controlled key with a more favourable number of near-collision keys. Even with the least restricted attack type presented in Table \ref{tab:nysiis0}, the computation of half a day can provide almost a 10\% success rate when attacking users.
